---
title: "Analysis of perspective taking data"
subtitle: "Analyses"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# Overview

All included measures are used as measures of empathy or to make conclusions about empathy. While some may be used to examine different facets of empathy, this distinction is a) not theoretically agreed upon, as there is little consensus around the structure of empathy, and therefore b) not necessarily reflected in their measurement (i.e., low correlations may represent poor convergent validity rather than good discriminant validity).

This study examines a) the reliability of these scales (internal consistency, test-retest reliability) relative to the original published estimates, and b) the risk of jingle fallacy (via correlations among [sub]scales).  

NB EQ subscales based on Lawrence et al., 2004.

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)
```

# Dependencies

```{r}

library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(forcats)
library(irr)
library(psych)
library(lavaan)
library(janitor)
library(ggplot2)
library(patchwork)
library(ggstance)
library(ggrain)
library(ggrepel)
library(scales)
library(mirt)
library(metafor)
library(strait)
library(correlation)
library(see)
library(insight)
library(purrr)
library(knitr)
library(kableExtra)

options(scipen=999)

dir.create("plots")

# every figure is written twice: a png for embedding, and a vector pdf of the same
# dimensions for submission. Takes the same arguments as ggsave(), with a .png
# filename; the pdf is written alongside it. cairo_pdf is used so that any unicode
# in the labels renders correctly, and dpi (which only applies to the png) is passed
# through by ggsave to the raster device only
ggsave_png_pdf <- function(filename, ...){
  ggsave(filename, ...)
  ggsave(str_replace(filename, "\\.png$", ".pdf"), ..., device = cairo_pdf)
}

# manuscript page geometry: A4 with 1 inch margins.
# NB the .docx is currently US Letter; for that, set page_width 8.5 and page_height 11
page_width  <- 8.27
page_height <- 11.69
page_margin <- 1
text_width  <- page_width  - 2 * page_margin
text_height <- page_height - 2 * page_margin

# Each figure is saved at the size at which it is displayed in the manuscript, so that
# its text is rendered at final size rather than being scaled down by the word
# processor. fig_size() takes the design dimensions of a layout (the canvas its panels
# were arranged for) and the fraction of the text area the figure occupies, and returns
# the display dimensions together with `scale`, the factor by which the design has
# shrunk. Text and point sizes are multiplied by `scale` so that the figure looks like
# the full-size design shrunk onto the page, rather than having oversized labels.
fig_size <- function(design_width, design_height, width = NULL, height = NULL){
  display_width <- if (!is.null(width)) {
    width * text_width
  } else {
    height * text_height * design_width / design_height
  }
  list(width  = display_width,
       height = display_width * design_height / design_width,
       scale  = display_width / design_width)
}

# base font size for a figure saved at `scale` of the size it was designed at
base_size <- function(fig) 11 * fig$scale

# display size of every figure, as a fraction of the text area
fig_trt         <- fig_size(6,  5,  width  = 0.8)
fig_alpha       <- fig_size(6,  5,  width  = 0.8)
fig_reliability <- fig_size(7,  6,  width  = 0.8)
fig_rain        <- fig_size(12, 13, width  = 1)     # totals; the subscale panels share its scale
fig_rain_sub    <- fig_size(12, 16, width  = 1)
fig_bounds      <- fig_size(12, 13, width  = 1)
fig_bounds_sub  <- fig_size(12, 16, width  = 1)
fig_pomp_sd     <- fig_size(8,  9,  width  = 0.8)
# The correlation matrices use coord_fixed(), so their panels are square and the canvas
# is not free to take any aspect ratio: it has to fit the square panel plus the room the
# row labels, legend and margins need beside it (roughly 0.8-1.2 in at these font sizes,
# measured from the rendered figures). Hence the width is given explicitly rather than
# derived from a design aspect ratio; too narrow and the square panel shrinks, leaving
# whitespace above and below it. `scale` still follows the height, so the text sizes are
# the same as they would be under the rules above.
fig_cor_hist    <- list(width = 6.12, height = 7.75, scale = 5.81/9)  # histogram + matrix
fig_cor_single  <- list(width = 6.27, height = 5.61, scale = 6.27/9)  # one matrix alone
fig_cor_pair    <- list(width = 4.33, height = 7.75, scale = 3.88/9)  # two matrices stacked
fig_cor_pt      <- list(width = 5.02, height = 4.30, scale = 5.02/7)  # one smaller matrix

# the same rules applied to the figures in the commented-out sections further down, so
# that they match if they are ever re-enabled: the portrait histogram-plus-matrix
# layouts are fitted to the text height unless that would overflow the text width
# (as it does for the 6 x 7 scale-only layouts), and the wider two-column T1 vs T2
# comparisons are fitted to the text width
fig_cor_scales     <- fig_size(6,    7, width  = 1)     # histogram + matrix, scales
fig_cor_subscales  <- fig_size(7,    9, height = 0.8)   # histogram + matrix, subscales
fig_cor_both       <- fig_size(9.35, 6, width  = 1)     # T1 and T2 side by side
fig_cor_both_sub   <- fig_size(13.2, 9, width  = 1)

```

# Load data

```{r}

data_processed <- read_csv("../data/processed/data_processed.csv") |>
  rename(PTP_sim = PTP_simple,
         PTP_rev = PTP_reversed,
         PTP_dbl = PTP_doublereversed) |>
  # display the Reading the Mind in the Eyes Test as "RMET" throughout
  rename_with(~ str_replace(.x, "^EYES", "RMET"))

data_processed_after_exclusions <- data_processed |>
  filter(exclude_master == "include")

data_sumscores <- data_processed_after_exclusions |>
  select(unique_id, timepoint, 
         SITES, 
         IRI_FS, IRI_EC, IRI_PT, IRI_PD, IRI_total,
         EQ_cog, EQ_aff, EQ_soc, EQ_total, 
         PET_total, 
         RMET_total, 
         PTP_sim, PTP_rev, PTP_dbl, PTP_total, 
         PTTA_total)

data_items <- data_processed_after_exclusions |>
  select(unique_id, 
         timepoint, 
         starts_with("IRI_"), 
         starts_with("EQ_"),
         starts_with("PET_"),
         starts_with("RMET_"),
         starts_with("PTP_"),
         starts_with("PTTA_"),
         -IRI_FS, -IRI_EC, -IRI_PT, -IRI_PD, -IRI_total,
         -EQ_cog, -EQ_aff, -EQ_soc, -EQ_total, 
         -PET_total, 
         -RMET_total, 
         -PTP_sim, -PTP_rev, -PTP_dbl, -PTP_total, 
         -PTTA_total, 
         -ends_with("_completeness"))

```

# Demographics

## Sample sizes and exclusions

```{r}

data_processed |>
  count(timepoint, exclude_master) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

## Analytic sample (timepoint 1)

```{r}

data_processed_after_exclusions |>
  filter(timepoint == 1) |>
  count(gender) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

data_processed_after_exclusions |>
  filter(timepoint == 1) |>
  dplyr::summarize(mean_age = mean(age),
                   sd_age = sd(age),
                   min_age = min(age),
                   max_age = max(age)) |>
  pivot_longer(cols = everything()) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

data_processed_after_exclusions |>
  distinct(unique_id, .keep_all = TRUE) |>
  ggplot(aes(age)) +
  geom_histogram(binwidth = 5) +
  theme_linedraw()

```

# Analyses

## Test-retest

$ICC_{2,1}$

### Results

```{r}

data_reshaped <- data_sumscores |>
  pivot_wider(id_cols = unique_id,
              names_from = timepoint,
              values_from = c(SITES, 
                              IRI_FS, IRI_EC, IRI_PT, IRI_PD, IRI_total,
                              EQ_cog, EQ_aff, EQ_soc, EQ_total, 
                              PET_total, 
                              RMET_total, 
                              PTP_sim, PTP_rev, PTP_dbl, PTP_total, 
                              PTTA_total))

tidy_icc_2_1 <- function(data, scale){
  res <- data |>
    select(starts_with(scale)) |>
    irr::icc(model = "twoway", type = "agreement", unit = "single",
             r0 = 0, conf.level = 0.95)
  
  tibble(scale = scale,
         icc_2.1 = res$value,
         ci_lower = res$lbound,
         ci_upper = res$ubound)
}

res <- bind_rows(
  tidy_icc_2_1(data_reshaped, "SITES"),
  tidy_icc_2_1(data_reshaped, "IRI_FS"),
  tidy_icc_2_1(data_reshaped, "IRI_EC"),
  tidy_icc_2_1(data_reshaped, "IRI_PT"),
  tidy_icc_2_1(data_reshaped, "IRI_PD"),
  tidy_icc_2_1(data_reshaped, "IRI_total"),
  tidy_icc_2_1(data_reshaped, "EQ_total"),
  tidy_icc_2_1(data_reshaped, "EQ_cog"),
  tidy_icc_2_1(data_reshaped, "EQ_aff"),
  tidy_icc_2_1(data_reshaped, "EQ_soc"),
  tidy_icc_2_1(data_reshaped, "PET_total"),
  tidy_icc_2_1(data_reshaped, "RMET_total"),
  tidy_icc_2_1(data_reshaped, "PTP_total"),
  tidy_icc_2_1(data_reshaped, "PTP_sim"),
  tidy_icc_2_1(data_reshaped, "PTP_rev"),
  tidy_icc_2_1(data_reshaped, "PTP_dbl"),
  tidy_icc_2_1(data_reshaped, "PTTA_total")
)

# keep the ICC[2,1] estimates for later disattenuation of the correlations
icc_2_1_results <- res

res |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

### Plots

#### Bar

```{r fig.height=4.18, fig.width=5.02}

p_trt_scales <- res |>
  filter(str_detect(scale, "SITES") | str_detect(scale, "_total")) |>
  mutate(scale = str_remove(scale, "_total")) |>
  ggplot(aes(icc_2.1, fct_rev(scale))) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_linerangeh(aes(xmin = ci_lower, xmax = ci_upper), position = position_dodge(width = .3)) +
  geom_point(position = position_dodge(width = .3)) +
  scale_x_continuous(breaks = breaks_pretty(n = 10),
                     limits = c(-.2, 1),
                     name = bquote("Test-Retest Reliability" ~ (ICC["2,1"]))) +
  theme_linedraw(base_size = base_size(fig_trt)) +
  ylab("Scale")

p_trt_subscales <- res |>
  filter(!str_detect(scale, "_total") & !str_detect(scale, "SITES")) |>
  mutate(scale = str_replace(scale, "_", " ")) |>
  mutate(scale = str_replace(scale, "doublereversed", "double")) |>
  ggplot(aes(icc_2.1, fct_rev(scale))) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_linerangeh(aes(xmin = ci_lower, xmax = ci_upper), position = position_dodge(width = .3)) +
  geom_point(position = position_dodge(width = .3)) +
  scale_x_continuous(breaks = breaks_pretty(n = 10),
                     limits = c(-.2, 1),
                     name = bquote("Test-Retest Reliability" ~ (ICC["2,1"]))) +
  theme_linedraw(base_size = base_size(fig_trt)) +
  ylab("Subscale")

p_trt_scales + 
  p_trt_subscales + 
  plot_layout(ncol = 1, heights = c(1, 1.35))

ggsave_png_pdf("plots/trt.png",
       width = fig_trt$width,
       height = fig_trt$height,
       dpi = 600)

```

#### Raincloud

```{r}

round_half_up_trailing <- function(x, digits = 2) {
  x_rounded <- round_half_up(x, digits = digits)
  sprintf("%.*f", digits, x_rounded)
}

res_print <- res |>
  mutate(across(where(is.numeric), ~ round_half_up_trailing(.x, digits = 2))) |>
  mutate(string = paste0("= ", icc_2.1, ", 95% CI [", ci_lower, ", ", ci_upper, "]")) |>
  select(scale, string)

data_reshaped_plotting <- data_sumscores |>
  pivot_longer(cols = c(SITES,
                        IRI_FS, IRI_EC, IRI_PT, IRI_PD, IRI_total,
                        EQ_cog, EQ_aff, EQ_soc, EQ_total,
                        PET_total,
                        RMET_total,
                        PTP_sim, PTP_rev, PTP_dbl, PTP_total,
                        PTTA_total),
               names_to = "scale",
               values_to = "score")

# theoretical minimum and maximum possible score for each (sub)scale. Used to
# express scores as POMP (percent of maximum possible): 100 * (x - min) / (max - min),
# and, together with the scoring structure (whether the score is a single item, a sum
# of items, or a mean of items, and how many items), to derive the feasible SD bounds
# in the section below.
# min/max derived from the item scoring in 2_processing.Rmd:
#   SITES      single item scored 1-5
#   IRI_*      7 items each 0-4 (28 items for the total)
#   EQ_cog     15 items, EQ_aff 12, EQ_soc 8, EQ_total 40, each item 0-2
#   PET_total  mean of 7 items each 1-5
#   RMET_total 36 items each 0-1
#   PTP_sim    3 items, PTP_rev 4, PTP_dbl 2, PTP_total 9, each item 0-1
#   PTTA_total 32 items each 0-1
scale_ranges <- tribble(
  ~scale,       ~score_min, ~score_max, ~scoring,     ~n_items,
  "SITES",      1,          5,          "singleitem", 1,
  "IRI_FS",     0,          28,         "sumscored",  7,
  "IRI_EC",     0,          28,         "sumscored",  7,
  "IRI_PT",     0,          28,         "sumscored",  7,
  "IRI_PD",     0,          28,         "sumscored",  7,
  "IRI_total",  0,          112,        "sumscored",  28,
  "EQ_cog",     0,          30,         "sumscored",  15,
  "EQ_aff",     0,          24,         "sumscored",  12,
  "EQ_soc",     0,          16,         "sumscored",  8,
  "EQ_total",   0,          80,         "sumscored",  40,
  "PET_total",  1,          5,          "meanscored", 7,
  "RMET_total", 0,          36,         "sumscored",  36,
  "PTP_sim",    0,          3,          "sumscored",  3,
  "PTP_rev",    0,          4,          "sumscored",  4,
  "PTP_dbl",    0,          2,          "sumscored",  2,
  "PTP_total",  0,          9,          "sumscored",  9,
  "PTTA_total", 0,          32,         "sumscored",  32
)

data_reshaped_plotting_pomp <- data_reshaped_plotting |>
  left_join(scale_ranges, by = "scale") |>
  mutate(pomp = 100 * (score - score_min) / (score_max - score_min))

# display titles for each (sub)scale
scale_titles <- c(
  SITES      = "Single Item Trait Empathy Scale",
  IRI_total  = "Interpersonal Reactivity Index",
  IRI_FS     = "IRI - Fantasy Subscale",
  IRI_EC     = "IRI - Empathic Concern Subscale",
  IRI_PT     = "IRI - Perspective Taking Subscale",
  IRI_PD     = "IRI - Personal Distress Subscale",
  EQ_total   = "Emotional Quotient",
  EQ_cog     = "EQ - Cognitive Empathy Subscale",
  EQ_aff     = "EQ - Affective Empathy Subscale",
  EQ_soc     = "EQ - Social Skills Subscale",
  PET_total  = "Pictoral Empathy Test",
  RMET_total = "Reading the Mind in the Eyes Test",
  PTP_total  = "Perspective Taking Protocol",
  PTP_sim    = "PTP - Simple Subscale",
  PTP_rev    = "PTP - Reversed Subscale",
  PTP_dbl    = "PTP - Double-Reversed Subscale",
  PTTA_total = "Perspective Taking Task for Adults"
)

# (sub)scales scored as small discrete counts, plotted with geom_rain's likert jitter
likert_scales <- c("SITES", "PTP_total", "PTP_sim", "PTP_rev", "PTP_dbl")

# helper to build a within-subject raincloud panel for one (sub)scale.
# yvar/ylab switch between raw scores and POMP; ylim (via coord_cartesian) gives
# the POMP plots a common 0-100 axis so proportionate variance is comparable.
make_raincloud <- function(data, scale_name, yvar = "score", ylab = "Score",
                           likert = FALSE, ylim = NULL) {
  p <- data |>
    filter(scale == scale_name) |>
    ggplot(aes(as.factor(timepoint), .data[[yvar]], fill = as.factor(timepoint))) +
    geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id", likert = likert,
              # the data points are drawn at a fixed size rather than one relative to
              # the panel, so they are scaled with the figure like the text is
              point.args = list(size = 1.5 * fig_rain$scale)) +
    # all four raincloud figures are displayed at the full text width and share a
    # design width, so they share a scale factor
    theme_classic(base_size = base_size(fig_rain)) +
    scale_fill_manual(values = c("dodgerblue", "darkorange")) +
    guides(fill = 'none', color = 'none') +
    ylab(ylab) +
    xlab("Time point") +
    ggtitle(bquote(.(scale_titles[[scale_name]]) * ":" ~ ICC["2,1"] ~
                     .(res_print |> filter(scale == scale_name) |> pull(string)))) +
    scale_y_continuous(breaks = scales::breaks_pretty(n = 6))
  if (!is.null(ylim)) p <- p + coord_cartesian(ylim = ylim)
  p
}

# total scores (IRI perspective-taking subscale moved to the subscales plot below)
scales_totals    <- c("IRI_total", "SITES", "PET_total", "EQ_total",
                      "RMET_total", "PTP_total", "PTTA_total")
# subscales of the multi-facet measures
scales_subscales <- c("IRI_FS", "IRI_EC", "IRI_PT", "IRI_PD",
                      "EQ_cog", "EQ_aff", "EQ_soc",
                      "PTP_sim", "PTP_rev", "PTP_dbl")

```

Total scores:

```{r fig.height=6.79, fig.width=6.27}

wrap_plots(
  map(scales_totals,
      ~ make_raincloud(data_reshaped_plotting, .x, likert = .x %in% likert_scales)),
  ncol = 2
)

ggsave_png_pdf("plots/raincloud_totals.png", width = fig_rain$width, height = fig_rain$height, dpi = 600)

```

Subscales:

```{r fig.height=8.36, fig.width=6.27}

wrap_plots(
  map(scales_subscales,
      ~ make_raincloud(data_reshaped_plotting, .x, likert = .x %in% likert_scales)),
  ncol = 2
)

ggsave_png_pdf("plots/raincloud_subscales.png", width = fig_rain_sub$width, height = fig_rain_sub$height, dpi = 600)

```

Total scores, converted to POMP (percent of maximum possible) so proportionate variance is comparable across measures:

```{r fig.height=6.79, fig.width=6.27}

wrap_plots(
  map(scales_totals,
      ~ make_raincloud(data_reshaped_plotting_pomp, .x,
                       yvar = "pomp", ylab = "POMP (%)", ylim = c(0, 100))),
  ncol = 2
)

ggsave_png_pdf("plots/raincloud_totals_pomp.png", width = fig_rain$width, height = fig_rain$height, dpi = 600)

```

Subscales, converted to POMP:

```{r fig.height=8.36, fig.width=6.27}

wrap_plots(
  map(scales_subscales,
      ~ make_raincloud(data_reshaped_plotting_pomp, .x,
                       yvar = "pomp", ylab = "POMP (%)", ylim = c(0, 100))),
  ncol = 2
)

ggsave_png_pdf("plots/raincloud_subscales_pomp.png", width = fig_rain_sub$width, height = fig_rain_sub$height, dpi = 600)

```

#### Mean and SD against the feasible SD bounds

On a bounded scale the mean constrains the SD, so the two are not independent: a (sub)scale whose mean sits close to a limit cannot show much dispersion. The `strait` package computes, in closed form, the smallest and largest sample SD consistent with a given mean, sample size, scale range and scoring structure. The bounds used here are the *sharp quasi-integer* ones: sharp in that they are attained rather than merely not exceeded (unlike the Bhatia-Davis / Popoviciu-type inequalities used previously, which ignore both the finite sample size and the granularity of the responses), and quasi-integer in that they respect the fact that item responses, and therefore sum scores, fall on an integer grid, while remaining defined at every mean rather than only at the GRIM-consistent ones.

The umbrella plots below show, for each (sub)scale, the feasible region of (mean, SD) pairs at Time 1 with the observed mean and SD overlaid; the shaded area is what the scale's structure rules out. The ceiling is the dome and the scalloped line along the bottom is the floor, whose cusps fall at the means an integer sum can hit exactly.

```{r}

# observed summary statistics for each (sub)scale in the Time 1 analytic sample,
# rounded to 2 decimals, i.e., the precision at which they would be reported
sd_bounds_dat <- data_reshaped_plotting |>
  filter(timepoint == 1) |>
  group_by(scale) |>
  summarise(n    = sum(!is.na(score)),
            mean = round_half_up(mean(score, na.rm = TRUE), digits = 2),
            sd   = round_half_up(sd(score,   na.rm = TRUE), digits = 2),
            .groups = "drop") |>
  left_join(scale_ranges, by = "scale") |>
  rename(l = score_min, u = score_max)

# BRIMMER: the sharp quasi-integer floor and ceiling for the SD given the mean, the
# scale limits, n and the scoring structure, plus the POMP transforms of both. Also
# returns a consistency verdict, which for data computed from the raw responses (as
# opposed to values transcribed from a paper) is expected to be TRUE throughout
sd_bounds_res <- sd_bounds_dat |>
  brimmer_multiple(Z = "quasiinteger", mean_digits = 2, sd_digits = 2) |>
  mutate(type  = if_else(str_detect(scale, "_total$") | scale == "SITES",
                         "Scale", "Subscale"),
         label = str_replace(str_remove(scale, "_total"), "_", " "))

sd_bounds_res |>
  select(scale, n, l, u, scoring, n_items, mean, sd, min_sd, max_sd,
         pomp_mean, pomp_sd_sharp, consistent) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

# one bounds curve per (sub)scale: the curves differ because l, u, n and the scoring
# structure differ
sd_bounds_curves <- sd_bounds_res |>
  split(~ scale) |>
  map(~ sd_bounds_curve(l = .x$l, u = .x$u, n = .x$n, Z = "quasiinteger",
                        scoring = .x$scoring, n_items = .x$n_items))

make_umbrella <- function(scale_name){
  plot_sd_bounds(sd_bounds_curves[[scale_name]],
                 points = sd_bounds_res |> filter(scale == scale_name),
                 title  = scale_titles[[scale_name]]) +
    # plot_sd_bounds() leaves the default theme in place, so its base size is set here
    # for the size the figure is displayed at (both panels share a design width)
    theme_grey(base_size = base_size(fig_bounds))
}

```

Total scores:

```{r fig.height=6.79, fig.width=6.27}

wrap_plots(map(scales_totals, make_umbrella), ncol = 2, guides = "collect") &
  theme(legend.position = "bottom")

ggsave_png_pdf("plots/sd_bounds_totals.png", width = fig_bounds$width, height = fig_bounds$height, dpi = 600)

```

Subscales:

```{r fig.height=8.36, fig.width=6.27}

wrap_plots(map(scales_subscales, make_umbrella), ncol = 2, guides = "collect") &
  theme(legend.position = "bottom")

ggsave_png_pdf("plots/sd_bounds_subscales.png", width = fig_bounds_sub$width, height = fig_bounds_sub$height, dpi = 600)

```

The umbrella is a different shape for every (sub)scale, so the raw SDs are not comparable across measures. The plot below puts them on a common footing by using the bounds themselves as the denominator: each (sub)scale's SD is expressed as its position within its own sharp band (0 = the floor, 1 = the ceiling), against its POMP mean. This replaces the previous Bhatia-Davis proportion, and answers the same question - how much of the dispersion available to it, given where its mean sits, does each measure actually use - but against a bound that is attainable rather than merely arithmetic. The feasible region is by construction the unit square; shaded regions are infeasible.

```{r fig.height=5.64, fig.width=5.02}

# with reference = "sharp" each point is normalised by its own bounds, so the curve
# argument is unused (it is only drawn for reference = "parity") but is still required
make_pomp_bounds_plot <- function(type_name){
  points <- sd_bounds_res |> filter(type == type_name)

  plot_sd_bounds_pomp(sd_bounds_curves[[1]],
                      points = points,
                      reference = "sharp",
                      title = paste0(type_name, "s")) +
    ggrepel::geom_text_repel(data = points,
                             aes(pomp_mean, pomp_sd_sharp, label = label),
                             size = 3 * fig_pomp_sd$scale,
                             max.overlaps = Inf, min.segment.length = 0) +
    # plot_sd_bounds_pomp() applies theme_minimal(); reapplied here at the size the
    # figure is displayed at
    theme_minimal(base_size = base_size(fig_pomp_sd))
}

make_pomp_bounds_plot("Scale") +
  make_pomp_bounds_plot("Subscale") +
  plot_layout(ncol = 1, guides = "collect") &
  theme(legend.position = "bottom")

ggsave_png_pdf("plots/pomp_mean_vs_sharp_sd_bound.png", width = fig_pomp_sd$width, height = fig_pomp_sd$height, dpi = 600)

```

## Internal consistency

Cronbach's $\alpha$

```{r}

tidy_alpha <- function(data, time, scale){
  res <- data |>
    filter(timepoint == time) |>
    dplyr::select(starts_with(scale)) |>
    psych::alpha()

  res2 <- res$feldt

  tibble(scale = scale,
         timepoint = time,
         alpha = res2$alpha$raw_alpha,
         ci_lower = res2$lower.ci$raw_alpha,
         ci_upper = res2$upper.ci$raw_alpha)
}

# variant that takes an explicit vector of items, for subscales whose items
# cannot be selected with a single starts_with() prefix
tidy_alpha_items <- function(data, time, scale, items){
  res <- data |>
    filter(timepoint == time) |>
    dplyr::select(all_of(items)) |>
    psych::alpha()

  res2 <- res$feldt

  tibble(scale = scale,
         timepoint = time,
         alpha = res2$alpha$raw_alpha,
         ci_lower = res2$lower.ci$raw_alpha,
         ci_upper = res2$upper.ci$raw_alpha)
}

# subscale item compositions (from processing.Rmd)
items_IRI_FS <- c("IRI_1", "IRI_5", "IRI_7", "IRI_12", "IRI_16", "IRI_26", "IRI_23")
items_IRI_EC <- c("IRI_2", "IRI_4", "IRI_9", "IRI_14", "IRI_18", "IRI_20", "IRI_22")
items_IRI_PT <- c("IRI_3", "IRI_8", "IRI_11", "IRI_15", "IRI_21", "IRI_25", "IRI_28")
items_IRI_PD <- c("IRI_6", "IRI_10", "IRI_13", "IRI_17", "IRI_19", "IRI_24", "IRI_27")
# EQ total is scored on 40 items; the social-skills items (EQ_30/31/33/51/53) are
# retained in the data for the EQ_soc subscale but are not part of the total score
items_EQ_total <- c("EQ_1", "EQ_4", "EQ_6", "EQ_8", "EQ_10", "EQ_11", "EQ_12", "EQ_14", "EQ_15", "EQ_18", "EQ_19", "EQ_21", "EQ_22", "EQ_25", "EQ_26", "EQ_27", "EQ_28", "EQ_29", "EQ_32", "EQ_34", "EQ_35", "EQ_36", "EQ_37", "EQ_38", "EQ_39", "EQ_41", "EQ_42", "EQ_43", "EQ_44", "EQ_46", "EQ_48", "EQ_49", "EQ_50", "EQ_52", "EQ_54", "EQ_55", "EQ_57", "EQ_58", "EQ_59", "EQ_60")
items_EQ_cog <- c("EQ_8", "EQ_19", "EQ_22", "EQ_25", "EQ_26", "EQ_35", "EQ_36", "EQ_41", "EQ_43", "EQ_44", "EQ_52", "EQ_54", "EQ_55", "EQ_58", "EQ_60")
items_EQ_aff <- c("EQ_1", "EQ_6", "EQ_18", "EQ_21", "EQ_32", "EQ_38", "EQ_39", "EQ_42", "EQ_46", "EQ_48", "EQ_50", "EQ_59")
items_EQ_soc <- c("EQ_14", "EQ_29", "EQ_30", "EQ_31", "EQ_33", "EQ_34", "EQ_51", "EQ_53")
items_PTP_sim <- c("PTP_1", "PTP_2", "PTP_3")
items_PTP_rev <- c("PTP_4", "PTP_5", "PTP_6", "PTP_7")
items_PTP_dbl <- c("PTP_8", "PTP_9")

# res <- bind_rows(
#   tidy_alpha(data = data_items, time = 1, scale = "IRI_"),
#   #tidy_alpha(data = data_items, time = 2, scale = "IRI_"),
#   tidy_alpha(data = data_items, time = 1, scale = "EQ_"),
#   #tidy_alpha(data = data_items, time = 2, scale = "EQ_"),
#   tidy_alpha(data = data_items, time = 1, scale = "PET_"),
#   #tidy_alpha(data = data_items, time = 2, scale = "PET_"),
#   tidy_alpha(data = data_items, time = 1, scale = "RMET_"),
#   #tidy_alpha(data = data_items, time = 2, scale = "RMET_")
#   tidy_alpha(data = data_items, time = 1, scale = "PTP_")
#   #tidy_alpha(data = data_items, time = 2, scale = "PTP_")
  
res <- bind_rows(
  #tidy_alpha(data = data_items, time = 1, scale = "SITES"),
  tidy_alpha(data = data_items, time = 1, scale = "IRI_"),
  tidy_alpha_items(data = data_items, time = 1, scale = "IRI_FS", items = items_IRI_FS),
  tidy_alpha_items(data = data_items, time = 1, scale = "IRI_EC", items = items_IRI_EC),
  tidy_alpha_items(data = data_items, time = 1, scale = "IRI_PT", items = items_IRI_PT),
  tidy_alpha_items(data = data_items, time = 1, scale = "IRI_PD", items = items_IRI_PD),
  tidy_alpha_items(data = data_items, time = 1, scale = "EQ_", items = items_EQ_total),
  tidy_alpha_items(data = data_items, time = 1, scale = "EQ_cog", items = items_EQ_cog),
  tidy_alpha_items(data = data_items, time = 1, scale = "EQ_aff", items = items_EQ_aff),
  tidy_alpha_items(data = data_items, time = 1, scale = "EQ_soc", items = items_EQ_soc),
  tidy_alpha(data = data_items, time = 1, scale = "PET_"),
  tidy_alpha(data = data_items, time = 1, scale = "RMET_"),
  tidy_alpha(data = data_items, time = 1, scale = "PTP_"),
  tidy_alpha_items(data = data_items, time = 1, scale = "PTP_sim", items = items_PTP_sim),
  tidy_alpha_items(data = data_items, time = 1, scale = "PTP_rev", items = items_PTP_rev),
  tidy_alpha_items(data = data_items, time = 1, scale = "PTP_dbl", items = items_PTP_dbl),
  tidy_alpha(data = data_items, time = 1, scale = "PTTA_")
)

res |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

### Plots

#### Bar

```{r fig.height=4.18, fig.width=5.02}

p_alpha_scales <- res |>
  filter(str_ends(scale, "_")) |>
  mutate(scale = str_remove(scale, "_")) |>
  ggplot(aes(alpha, fct_rev(scale))) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_linerangeh(aes(xmin = ci_lower, xmax = ci_upper), position = position_dodge(width = .3)) +
  geom_point(position = position_dodge(width = .3)) +
  scale_x_continuous(breaks = breaks_pretty(n = 10),
                     limits = c(-.2, 1),
                     name = bquote("Internal Consistency" ~ (alpha))) +
  theme_linedraw(base_size = base_size(fig_alpha)) +
  ylab("Scale")

p_alpha_subscales <- res |>
  filter(!str_ends(scale, "_")) |>
  mutate(scale = str_replace(scale, "_", " ")) |>
  ggplot(aes(alpha, fct_rev(scale))) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_linerangeh(aes(xmin = ci_lower, xmax = ci_upper), position = position_dodge(width = .3)) +
  geom_point(position = position_dodge(width = .3)) +
  scale_x_continuous(breaks = breaks_pretty(n = 10),
                     limits = c(-.2, 1),
                     name = bquote("Internal Consistency" ~ (alpha))) +
  theme_linedraw(base_size = base_size(fig_alpha)) +
  ylab("Subscale")

p_alpha_scales +
  p_alpha_subscales +
  plot_layout(ncol = 1, heights = c(1, 1.35))

ggsave_png_pdf("plots/internal_consistency.png",
       width = fig_alpha$width,
       height = fig_alpha$height,
       dpi = 600)

```

#### Combined

```{r fig.height=4.3, fig.width=5.02}

# harmonise (sub)scale labels across the two reliability tables: the ICC table
# names full scales "PTP_total" etc. while the alpha table names them "PTP_";
# subscale names (e.g. "PTP_sim") already match across the two
clean_label <- function(scale){
  scale |>
    str_remove("_total$") |>
    str_remove("_$") |>
    str_replace("_", " ")
}

reliability_combined <- bind_rows(
  icc_2_1_results |>
    transmute(label = clean_label(scale), estimate = icc_2.1, ci_lower, ci_upper, metric = "icc"),
  res |>  # alpha (internal consistency) results from the chunk above
    transmute(label = clean_label(scale), estimate = alpha, ci_lower, ci_upper, metric = "alpha")
) |>
  mutate(type = if_else(str_detect(label, " "), "Subscale", "Scale"),
         metric = factor(metric, levels = c("icc", "alpha")))

plot_reliability_combined <- function(data, ylab){
  ggplot(data, aes(estimate, fct_rev(label), colour = metric)) +
    geom_vline(xintercept = 0, linetype = "dotted") +
    geom_vline(xintercept = 0.70, linetype = "dashed") +
    geom_linerangeh(aes(xmin = ci_lower, xmax = ci_upper), position = position_dodgev(height = .6)) +
    geom_point(position = position_dodgev(height = .6)) +
    scale_x_continuous(breaks = breaks_pretty(n = 10),
                       limits = c(-.2, 1),
                       name = "Reliability") +
    scale_colour_manual(name = NULL,
                        values = c(icc = "dodgerblue", alpha = "darkorange"),
                        labels = c(expression("Test-Retest Reliability" ~ (ICC["2,1"])),
                                   expression("Internal Consistency" ~ (alpha)))) +
    theme_linedraw(base_size = base_size(fig_reliability)) +
    ylab(ylab)
}

plot_reliability_combined(filter(reliability_combined, type == "Scale"), "Scale") +
  plot_reliability_combined(filter(reliability_combined, type == "Subscale"), "Subscale") +
  plot_layout(ncol = 1, heights = c(1, 1.35), guides = "collect") &
  theme(legend.position = "bottom")

ggsave_png_pdf("plots/reliability_combined.png",
       width = fig_reliability$width,
       height = fig_reliability$height,
       dpi = 600)

```

## Correlations T1

#### Both scales and subscales

```{r fig.height=4.5}

all_cors <- data_sumscores |>
  filter(timepoint == 1) %>%
  select(-timepoint, -unique_id) %>%
  #rename_with(~ str_remove(.x, "_total")) %>%
  select(order(colnames(.))) |>
  correlation()

res <- all_cors |>
  as.data.frame() |>
  select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p) |>
  mutate(includes_ptp = if_else(str_detect(Parameter1, "PTP_") | str_detect(Parameter2, "PTP_"), "Correlation between PTP and other measures", "Correlation between all other measures"),
         includes_ptp = if_else(str_detect(Parameter1, "PTP_") & str_detect(Parameter2, "PTP_"), "PTP-self", includes_ptp))

res |>
  mutate(p = insight::format_p(p)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

p_hist_t1 <- 
  res |>
  filter(includes_ptp != "PTP-self") |>
  ggplot(aes(r)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_histogram(binwidth = 0.1, boundary = 0) +
  scale_x_continuous(limits = c(-1, 1), 
                     name = "Correlation", 
                     breaks = scales::breaks_pretty(n = 10)) + 
  scale_y_continuous(name = "Frequency", 
                     breaks = scales::breaks_pretty(n = 7)) + 
  theme_linedraw(base_size = base_size(fig_cor_hist)) +
  theme(panel.grid.minor.y = element_blank()) +
  facet_wrap(~ includes_ptp, ncol = 1)

#p0
  
# desired display order for the matrices: each full scale immediately above its own
# subscales, with the PTP placed first so it sits at the top-left of the matrix and
# the remaining (non-PTP) measures following in alphabetical order
measure_order <- c("PTP_total", "PTP_sim", "PTP_rev", "PTP_dbl",
                   "EQ_total", "EQ_cog", "EQ_aff", "EQ_soc",
                   "IRI_total", "IRI_FS", "IRI_EC", "IRI_PT", "IRI_PD",
                   "PET_total",
                   "PTTA_total",
                   "RMET_total",
                   "SITES")

# helper to blank out the redundant half of a correlation matrix produced by
# summary(..., redundant = TRUE), so that each correlation is displayed only once.
# summary(redundant = FALSE) also drops the redundant half, but reverses the column
# order in doing so, which breaks the intended measure_order layout of the matrix
keep_triangle <- function(cormatrix, which = "lower"){
  measures <- cormatrix$Parameter
  for (i in seq_along(measures)) {
    for (j in seq_along(measures)) {
      redundant_cell <- if (which == "lower") j >= i else j <= i
      if (redundant_cell) cormatrix[i, measures[j]] <- NA_real_
    }
  }
  cormatrix
}

# draw a correlation matrix at the size it is displayed at in the manuscript. The
# see/correlation defaults (geom_text size 3.88, point size range 5-15, theme base size
# 11) are tuned for a much larger canvas, so all three are multiplied by the figure's
# scale factor: the result is what the full-size matrix looks like shrunk onto the page,
# rather than a small panel with oversized labels and overlapping points
plot_cormatrix <- function(cormatrix, fig, title = ""){
  cormatrix |>
    plot(show_data = "points",
         stars = FALSE,
         text  = list(size = 3.88 * fig$scale),
         scale = list(range = c(5, 15) * fig$scale)) +
    theme_linedraw(base_size = base_size(fig)) +
    # the cells of a correlation matrix are meaningless as rectangles: one unit on the
    # x axis is one unit on the y axis, so the panel is square
    coord_fixed(ratio = 1) +
    ggtitle(title)
}

# code repeated in order to use the rename, which screws up the table but is needed for the plot
cormat_t1 <- data_sumscores |>
  filter(timepoint == 1) |>
  select(all_of(measure_order)) |>
  rename_with(~ str_remove(.x, "_total")) |>
  rename_with(~ str_replace(.x, "_", "\n")) |>
  correlation() %>%
  #mutate(across(where(is.numeric), ~ round_half_up(., 2))) |>
  summary(redundant = TRUE)

# the same matrix with the redundant upper triangle (and the diagonal) omitted. Both
# are drawn where they are used, since each figure displays them at a different size
cormat_t1_triangle <- keep_triangle(cormat_t1, "lower")

#p0 + coord_fixed(ratio = 1)

# scale_cors |>
#   summary() |>
#   plot(show_data = "points",
#        stars = FALSE) +
#   theme_linedraw() +
#   ggtitle("") +
#   coord_fixed(ratio = 1)

average_cors_all <- res |>
  dplyr::summarize(mean_r = mean(r),
                   sd_r = sd(r),
                   median_r = median(r),
                   mad_r = mad(r),
                   min_r = min(r),
                   max_r = max(r)) 

average_cors_all |>
  round_half_up(digits = 2) |>
  kable() |>
  kable_classic(full_width = FALSE)

```

```{r fig.height=7.75, fig.width=6.12}

p_hist_t1 + ggtitle("Correlation histogram") +
  plot_cormatrix(cormat_t1, fig_cor_hist, "Correlation matrix") +
  plot_layout(ncol = 1, heights = c(.4, 1))

ggsave_png_pdf("plots/cor_all_t1.png",
       width = fig_cor_hist$width,
       height = fig_cor_hist$height,
       dpi = 600)

```

The same matrix with only the lower triangle printed, i.e., each correlation shown once rather than twice.

```{r fig.height=5.61, fig.width=6.27}

plot_cormatrix(cormat_t1_triangle, fig_cor_single, "Correlation matrix")

ggsave_png_pdf("plots/cor_all_t1_triangle.png",
       width = fig_cor_single$width,
       height = fig_cor_single$height,
       dpi = 600)

```

##### Spearman's rho robustness test

The correlations above are Pearson's *r*. Several of the (sub)scales are bounded, coarse, and skewed (e.g., the PTP subscales are counts of 2-4 binary items), so the analyses are repeated with Spearman's rho, which is sensitive only to monotonic association and is robust to the non-normality and to outliers.

```{r fig.height=4.5}

all_cors_spearman <- data_sumscores |>
  filter(timepoint == 1) %>%
  select(-timepoint, -unique_id) %>%
  select(order(colnames(.))) |>
  correlation(method = "spearman")

res_spearman <- all_cors_spearman |>
  as.data.frame() |>
  select(Parameter1, Parameter2, rho, ci_low = CI_low, ci_high = CI_high, p) |>
  mutate(includes_ptp = if_else(str_detect(Parameter1, "PTP_") | str_detect(Parameter2, "PTP_"), "Correlation between PTP and other measures", "Correlation between all other measures"),
         includes_ptp = if_else(str_detect(Parameter1, "PTP_") & str_detect(Parameter2, "PTP_"), "PTP-self", includes_ptp))

res_spearman |>
  mutate(p = insight::format_p(p)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

p_hist_spearman_t1 <-
  res_spearman |>
  filter(includes_ptp != "PTP-self") |>
  ggplot(aes(rho)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_histogram(binwidth = 0.1, boundary = 0) +
  scale_x_continuous(limits = c(-1, 1),
                     name = "Correlation (Spearman's rho)",
                     breaks = scales::breaks_pretty(n = 10)) +
  scale_y_continuous(name = "Frequency",
                     breaks = scales::breaks_pretty(n = 7)) +
  theme_linedraw(base_size = base_size(fig_cor_hist)) +
  theme(panel.grid.minor.y = element_blank()) +
  facet_wrap(~ includes_ptp, ncol = 1)

# code repeated in order to use the rename, which screws up the table but is needed for the plot
cormat_spearman_t1_triangle <- data_sumscores |>
  filter(timepoint == 1) |>
  select(all_of(measure_order)) |>
  rename_with(~ str_remove(.x, "_total")) |>
  rename_with(~ str_replace(.x, "_", "\n")) |>
  correlation(method = "spearman") |>
  summary(redundant = TRUE) |>
  keep_triangle("lower")

average_cors_all_spearman <- res_spearman |>
  dplyr::summarize(mean_rho = mean(rho),
                   sd_rho = sd(rho),
                   median_rho = median(rho),
                   mad_rho = mad(rho),
                   min_rho = min(rho),
                   max_rho = max(rho))

average_cors_all_spearman |>
  round_half_up(digits = 2) |>
  kable() |>
  kable_classic(full_width = FALSE)

# agreement between the two sets of coefficients across all pairs of (sub)scales
res |>
  select(Parameter1, Parameter2, r) |>
  left_join(res_spearman |> select(Parameter1, Parameter2, rho),
            by = c("Parameter1", "Parameter2")) |>
  dplyr::summarize(`correlation between r and rho` = cor(r, rho),
                   `mean |r - rho|` = mean(abs(r - rho)),
                   `max |r - rho|` = max(abs(r - rho))) |>
  round_half_up(digits = 2) |>
  kable() |>
  kable_classic(full_width = FALSE)

```

```{r fig.height=7.75, fig.width=6.12}

p_hist_spearman_t1 + ggtitle("Correlation histogram (Spearman's rho)") +
  plot_cormatrix(cormat_spearman_t1_triangle, fig_cor_hist, "Correlation matrix (Spearman's rho)") +
  plot_layout(ncol = 1, heights = c(.4, 1))

ggsave_png_pdf("plots/cor_all_t1_spearman.png",
       width = fig_cor_hist$width,
       height = fig_cor_hist$height,
       dpi = 600)

```

The Spearman coefficients are near-identical to the Pearson ones (see the agreement table above), and the pattern of results is unchanged: the correlations involving the PTP remain close to zero while those among the other measures remain moderate to large. The conclusions are therefore not an artefact of the distributional properties of the (sub)scales.

#### Both scales and subscales - disattenuated for test-retest reliability

Each observed correlation is corrected for attenuation due to (un)reliability using the test-retest reliability (ICC[2,1]) of each measure in the pair: $r_{disattenuated} = r / \sqrt{ICC_x \cdot ICC_y}$. This estimates the correlation between the temporally stable (trait) components of the two measures.

Note that disattenuation is unstable when reliabilities are low: where a measure's test-retest reliability is near zero (notably the PTP total and subscales, ICC[2,1] <= .33), the corrected values are inflated and can exceed |1|. Such values should be read as "no reliable common signal to recover" rather than as point estimates. The table below reports the exact (unclamped) disattenuated values; the accompanying matrix plot clamps them to the valid correlation range [-1, 1] purely for display, so that the out-of-range PTP part-whole cells do not dominate the colour and point-size scales.

```{r}

# look up table of test-retest reliabilities (from the Test-retest section)
icc_lookup <- icc_2_1_results |>
  select(scale, icc = icc_2.1)

res_disattenuated <- all_cors |>
  as.data.frame() |>
  select(Parameter1, Parameter2, r) |>
  # attach the ICC[2,1] of each measure in the pair
  left_join(icc_lookup, by = c("Parameter1" = "scale")) |>
  rename(icc_1 = icc) |>
  left_join(icc_lookup, by = c("Parameter2" = "scale")) |>
  rename(icc_2 = icc) |>
  # correct for attenuation
  mutate(r_disattenuated = r / sqrt(icc_1 * icc_2))

res_disattenuated |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

```{r fig.height=7.75, fig.width=4.33}

# ICC[2,1] lookup keyed by the SAME renamed labels used on the plot axes,
# so it can be matched against the correlation object's Parameter1/Parameter2
icc_renamed <- icc_2_1_results |>
  mutate(scale = str_remove(scale, "_total"),
         scale = str_replace(scale, "_", "\n")) |>
  select(scale, icc = icc_2.1)

cormat_disattenuated_t1 <- data_sumscores |>
  filter(timepoint == 1) |>
  select(all_of(measure_order)) |>
  rename_with(~ str_remove(.x, "_total")) |>
  rename_with(~ str_replace(.x, "_", "\n")) |>
  correlation() %>%
  # disattenuate each correlation by the test-retest reliabilities of the pair,
  # r_disattenuated = r / sqrt(ICC_x * ICC_y), then clamp to the valid correlation
  # range [-1, 1] for display. Exact values (which can exceed |1| where a measure's
  # reliability is low, e.g. the PTP) are reported in the table above.
  mutate(r = r / sqrt(icc_renamed$icc[match(Parameter1, icc_renamed$scale)] *
                      icc_renamed$icc[match(Parameter2, icc_renamed$scale)]),
         r = pmax(pmin(r, 1), -1)) |>
  #mutate(across(where(is.numeric), ~ round_half_up(., 2))) |>
  summary(redundant = TRUE)

# same matrix with the redundant upper triangle (and the diagonal) omitted
cormat_disattenuated_t1_triangle <- keep_triangle(cormat_disattenuated_t1, "lower")

# these figures stack two matrices, so each is displayed at half the height and a
# third of the width of the single-matrix figures above, and is drawn accordingly
plot_cormatrix(cormat_t1, fig_cor_pair, "Observed correlations") +
  plot_cormatrix(cormat_disattenuated_t1, fig_cor_pair,
                 "Disattenuated for test-retest reliability") +
  plot_layout(ncol = 1)

ggsave_png_pdf("plots/cor_all_disattenuated_t1.png",
       width = fig_cor_pair$width,
       height = fig_cor_pair$height,
       dpi = 600)

```

The same two matrices with only the lower triangle printed, i.e., each correlation shown once rather than twice.

```{r fig.height=7.75, fig.width=4.33}

plot_cormatrix(cormat_t1_triangle, fig_cor_pair, "Observed correlations") +
  plot_cormatrix(cormat_disattenuated_t1_triangle, fig_cor_pair,
                 "Disattenuated for test-retest reliability") +
  plot_layout(ncol = 1)

ggsave_png_pdf("plots/cor_all_disattenuated_t1_triangle.png",
       width = fig_cor_pair$width,
       height = fig_cor_pair$height,
       dpi = 600)

```

##### Spearman's rho robustness test

The disattenuation is repeated using Spearman's rho in place of Pearson's *r*. Note that this is an approximation: the correction assumes the reliability coefficient and the correlation are on the same (product-moment) footing, whereas the ICC[2,1] used here is a product-moment-type coefficient while rho is rank-based. It is reported as a robustness check on the disattenuated pattern, not as an exact estimate.

```{r}

res_spearman_disattenuated <- all_cors_spearman |>
  as.data.frame() |>
  select(Parameter1, Parameter2, rho) |>
  # attach the ICC[2,1] of each measure in the pair
  left_join(icc_lookup, by = c("Parameter1" = "scale")) |>
  rename(icc_1 = icc) |>
  left_join(icc_lookup, by = c("Parameter2" = "scale")) |>
  rename(icc_2 = icc) |>
  # correct for attenuation
  mutate(rho_disattenuated = rho / sqrt(icc_1 * icc_2))

res_spearman_disattenuated |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

```{r fig.height=7.75, fig.width=4.33}

# as above, the exact (unclamped) values are in the table; the matrix clamps them
# to [-1, 1] purely for display
cormat_spearman_disattenuated_t1_triangle <- data_sumscores |>
  filter(timepoint == 1) |>
  select(all_of(measure_order)) |>
  rename_with(~ str_remove(.x, "_total")) |>
  rename_with(~ str_replace(.x, "_", "\n")) |>
  correlation(method = "spearman") %>%
  mutate(rho = rho / sqrt(icc_renamed$icc[match(Parameter1, icc_renamed$scale)] *
                          icc_renamed$icc[match(Parameter2, icc_renamed$scale)]),
         rho = pmax(pmin(rho, 1), -1)) |>
  summary(redundant = TRUE) |>
  keep_triangle("lower")

plot_cormatrix(cormat_spearman_t1_triangle, fig_cor_pair,
               "Observed correlations (Spearman's rho)") +
  plot_cormatrix(cormat_spearman_disattenuated_t1_triangle, fig_cor_pair,
                 "Disattenuated for test-retest reliability (Spearman's rho)") +
  plot_layout(ncol = 1)

ggsave_png_pdf("plots/cor_all_disattenuated_t1_spearman.png",
       width = fig_cor_pair$width,
       height = fig_cor_pair$height,
       dpi = 600)

```

As with the observed correlations, using Spearman's rho leaves the disattenuated pattern unchanged. The same instability applies here: because the PTP's test-retest reliability is near zero, correcting by it inflates the magnitude of its correlations erratically (several exceed |1| before clamping, and their signs are unstable across the PTP subscales), which reflects division by a near-zero denominator rather than a recovered common signal with the other measures.

#### Moderator meta-analysis: PTP vs non-PTP correlations

Each Time 1 correlation is treated as an effect size, Fisher r-to-z transformed (variance $1/(n-3)$), and entered into a mixed-effects meta-analysis with a binary moderator: whether the pair involves the PTP (or one of its subscales) with another measure, versus a correlation among two non-PTP (sub)scales. Correlations within the same instrument (a scale with its own subscales, and subscales of the same scale with one another) are part-whole / non-independent and are excluded, leaving only cross-instrument correlations. The analysis is run twice: on the observed correlations and on the correlations disattenuated for test-retest reliability.

```{r}

# strip subscale/total suffixes to identify each measure's parent instrument
strip_subscale <- function(x) str_remove(x, "_(total|FS|EC|PT|PD|cog|aff|soc|sim|rev|dbl)$")

meta_dat <- all_cors |>
  as.data.frame() |>
  select(Parameter1, Parameter2, r, n = n_Obs) |>
  left_join(icc_2_1_results |> transmute(scale, icc1 = icc_2.1), by = c("Parameter1" = "scale")) |>
  left_join(icc_2_1_results |> transmute(scale, icc2 = icc_2.1), by = c("Parameter2" = "scale")) |>
  mutate(r_disattenuated = r / sqrt(icc1 * icc2),
         # exclude within-instrument (part-whole / non-independent) correlations
         within_instrument = strip_subscale(Parameter1) == strip_subscale(Parameter2),
         # moderator: does the pair involve the PTP (or a PTP subscale)?
         moderator = if_else(str_detect(Parameter1, "^PTP") | str_detect(Parameter2, "^PTP"),
                             "PTP with other measures", "Among non-PTP measures")) |>
  filter(!within_instrument) |>
  mutate(moderator = factor(moderator, levels = c("Among non-PTP measures", "PTP with other measures")))

# Fisher r-to-z (clamp to avoid atanh(+/-1) = Inf for any over-corrected value)
fisher_z <- function(data, r_col){
  data |>
    mutate(ri = pmax(pmin(.data[[r_col]], 0.999), -0.999),
           yi = atanh(ri),
           vi = 1 / (n - 3))
}

# fit the moderator model, plus a version with cluster-robust standard errors.
# the effect sizes are dyadic (each correlation involves two measures), so they are
# not independent; we cluster on one member of each pair to get robust SEs that
# account for the shared-measure dependency
fit_meta <- function(r_col){
  dat <- fisher_z(meta_dat, r_col)
  model <- rma(yi, vi, mods = ~ moderator, data = dat)
  list(model = model,
       robust = robust(model, cluster = dat$Parameter1))
}

m_observed      <- fit_meta("r")
m_disattenuated <- fit_meta("r_disattenuated")

# number of effect sizes per group
k_by_group <- meta_dat |> count(moderator, name = "k")

# pooled estimate for each moderator group, back-transformed from Fisher z to
# Pearson's r together with its 95% CI (both model-based and cluster-robust)
preds_r <- function(fit, label){
  pm <- predict(fit$model,  newmods = c(0, 1))   # 0 = non-PTP (reference), 1 = PTP
  pr <- predict(fit$robust, newmods = c(0, 1))
  tibble(analysis = label,
         moderator = levels(meta_dat$moderator),
         r               = tanh(pm$pred),
         ci_lower        = tanh(pm$ci.lb),
         ci_upper        = tanh(pm$ci.ub),
         ci_lower_robust = tanh(pr$ci.lb),
         ci_upper_robust = tanh(pr$ci.ub))
}

bind_rows(
  preds_r(m_observed, "Observed correlations"),
  preds_r(m_disattenuated, "Disattenuated correlations")
) |>
  left_join(k_by_group, by = "moderator") |>
  mutate(across(c(r, starts_with("ci_")), ~ round_half_up(.x, digits = 2)),
         `r [95% CI]`          = paste0(r, " [", ci_lower, ", ", ci_upper, "]"),
         `r [95% CI] (robust)` = paste0(r, " [", ci_lower_robust, ", ", ci_upper_robust, "]")) |>
  select(analysis, moderator, k, `r [95% CI]`, `r [95% CI] (robust)`) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

# moderator test (difference between the two groups), with model-based and
# cluster-robust p-values (the test statistic is scale-free, so it is unchanged
# by the r-to-z transformation)
tibble(analysis = c("Observed correlations", "Disattenuated correlations"),
       `p (model)`  = c(m_observed$model$pval[2],  m_disattenuated$model$pval[2]),
       `p (robust)` = c(m_observed$robust$pval[2], m_disattenuated$robust$pval[2])) |>
  mutate(across(starts_with("p"), ~ insight::format_p(.x, stars = FALSE))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

All estimates are back-transformed from Fisher's z to Pearson's r for reporting: the table gives each group's pooled correlation with its 95% CI, and the moderator test (the difference between groups) is reported as a p-value, which is unchanged by the r-to-z transformation. In both analyses the correlations involving the PTP are far weaker than those among the other measures: the moderator captures essentially the whole of the (already weak) convergence in this battery. Because the effect sizes are dyadic and not fully independent (each measure appears in several pairs), we report cluster-robust 95% CIs and p-values (clustering on one member of each pair) alongside the model-based ones; the robust intervals are similar and the moderator remains highly significant in both the observed and disattenuated analyses. (The disattenuated analysis uses the observed-r sampling variance, so all of its intervals are approximate.)

##### Sensitivity analysis: excluding the RMET

The RMET itself has poor and contested psychometric properties (Higgins et al., 2023, 2024), so its inclusion could weaken the non-PTP comparison group. We therefore repeat the moderator meta-analysis after dropping every correlation that involves the RMET.

```{r}

meta_dat_sens <- meta_dat |>
  filter(Parameter1 != "RMET_total", Parameter2 != "RMET_total")

fit_sens <- function(r_col){
  dat   <- fisher_z(meta_dat_sens, r_col)
  model <- rma(yi, vi, mods = ~ moderator, data = dat)
  list(model = model, robust = robust(model, cluster = dat$Parameter1))
}

s_observed      <- fit_sens("r")
s_disattenuated <- fit_sens("r_disattenuated")

k_by_group_sens <- meta_dat_sens |> count(moderator, name = "k")

bind_rows(
  preds_r(s_observed, "Observed correlations"),
  preds_r(s_disattenuated, "Disattenuated correlations")
) |>
  left_join(k_by_group_sens, by = "moderator") |>
  mutate(across(c(r, starts_with("ci_")), ~ round_half_up(.x, digits = 2)),
         `r [95% CI]`          = paste0(r, " [", ci_lower, ", ", ci_upper, "]"),
         `r [95% CI] (robust)` = paste0(r, " [", ci_lower_robust, ", ", ci_upper_robust, "]")) |>
  select(analysis, moderator, k, `r [95% CI]`, `r [95% CI] (robust)`) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

tibble(analysis = c("Observed correlations", "Disattenuated correlations"),
       `p (model)`  = c(s_observed$model$pval[2],  s_disattenuated$model$pval[2]),
       `p (robust)` = c(s_observed$robust$pval[2], s_disattenuated$robust$pval[2])) |>
  mutate(across(starts_with("p"), ~ insight::format_p(.x, stars = FALSE))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

Excluding the RMET, if anything, sharpens the contrast: the non-PTP measures cohere slightly more once the RMET is removed (*r* = .31 observed, .39 disattenuated), the PTP is unchanged (*r* ≈ .01–.03), and the moderator remains highly significant.

<!-- #### Scale correlations -->

<!-- ```{r fig.height=4.5} -->

<!-- scale_cors <- dat |> -->
<!--   select(SITES, ends_with("_total")) |> -->
<!--   rename_with(~ str_remove(.x, "_total")) %>% -->
<!--   select(order(colnames(.))) |> -->
<!--   correlation() -->

<!-- res <- scale_cors |> -->
<!--   as.data.frame() |> -->
<!--   select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p)  -->

<!-- res |> -->
<!--   mutate(p = insight::format_p(p)) |> -->
<!--   mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |> -->
<!--   kable(align = "r") |> -->
<!--   kable_classic(full_width = FALSE) -->

<!-- p1_t1 <-  -->
<!--   ggplot(res, aes(r)) + -->
<!--   geom_vline(xintercept = 0, linetype = "dashed") + -->
<!--   geom_histogram(binwidth = 0.1, boundary = 0) + -->
<!--   scale_x_continuous(limits = c(-1, 1),  -->
<!--                      name = "Correlation",  -->
<!--                      breaks = scales::breaks_pretty(n = 10)) +  -->
<!--   scale_y_continuous(name = "Frequency",  -->
<!--                      breaks = scales::breaks_pretty(n = 7)) +  -->
<!--   theme_linedraw(base_size = base_size(fig_cor_scales)) + -->
<!--   theme(panel.grid.minor.y = element_blank()) -->

<!-- #p1 -->

<!-- p2_t1 <-  -->
<!--   scale_cors |> -->
<!--   summary(redundant = TRUE) |> -->
<!--   plot_cormatrix(fig_cor_scales) -->

<!-- #p2 + coord_fixed(ratio = 1) -->

<!-- # scale_cors |> -->
<!-- #   summary() |> -->
<!-- #   plot(show_data = "points", -->
<!-- #        stars = FALSE) + -->
<!-- #   theme_linedraw() + -->
<!-- #   ggtitle("") + -->
<!-- #   coord_fixed(ratio = 1) -->

<!-- average_cors_all <- res |> -->
<!--   dplyr::summarize(mean_r = mean(r), -->
<!--                    sd_r = sd(r), -->
<!--                    median_r = median(r), -->
<!--                    mad_r = mad(r), -->
<!--                    min_r = min(r), -->
<!--                    max_r = max(r))  -->

<!-- average_cors_all |> -->
<!--   round_half_up(digits = 2) |> -->
<!--   kable() |> -->
<!--   kable_classic(full_width = FALSE) -->

<!-- ``` -->

<!-- ```{r fig.height=7.32, fig.width=6.27} -->

<!-- p1_t1 + ggtitle("Correlation histogram") + -->
<!--   p2_t1 + ggtitle("Correlation matrix") +  -->
<!--   plot_layout(ncol = 1, heights = c(.4, 1)) -->

<!-- ggsave_png_pdf("plots/cor_scales_t1.png", -->
<!--        width = fig_cor_scales$width, -->
<!--        height = fig_cor_scales$height, -->
<!--        dpi = 600) -->

<!-- ``` -->

<!-- #### Subscale correlations -->

<!-- ```{r fig.height=6, fig.width=11} -->

<!-- subscale_cors <- dat |> -->
<!--   select(SITES,  -->
<!--          IRI_FS, IRI_EC, IRI_PT, IRI_PD,  -->
<!--          EQ_cog, EQ_aff, EQ_soc,  -->
<!--          PET_total, -->
<!--          PTP_sim, PTP_rev, PTP_dbl) |> -->
<!--   rename_with(~ str_remove(.x, "_total")) |> -->
<!--   correlation()  -->

<!-- subscale_cors |> -->
<!--   as.data.frame() |> -->
<!--   select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p) |> -->
<!--   mutate(p = insight::format_p(p)) |> -->
<!--   mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |> -->
<!--   kable(align = "r") |> -->
<!--   kable_classic(full_width = FALSE) -->

<!-- p3_t1 <-  -->
<!--   ggplot(subscale_cors, aes(r)) + -->
<!--   geom_vline(xintercept = 0, linetype = "dashed") + -->
<!--   geom_histogram(binwidth = 0.1, boundary = 0) + -->
<!--   scale_x_continuous(limits = c(-1, 1),  -->
<!--                      name = "Correlation",  -->
<!--                      breaks = scales::breaks_pretty(n = 10)) +  -->
<!--   scale_y_continuous(name = "Frequency",  -->
<!--                      breaks = scales::breaks_pretty(n = 7)) +  -->
<!--   theme_linedraw(base_size = base_size(fig_cor_subscales)) + -->
<!--   theme(panel.grid.minor.y = element_blank()) -->

<!-- #p3_t1 -->

<!-- # code repeated in order to use the rename, which screws up the table but is needed for the plot -->
<!-- p4_t1 <- dat |> -->
<!--   select(SITES,  -->
<!--          IRI_FS, IRI_EC, IRI_PT, IRI_PD,  -->
<!--          EQ_cog, EQ_aff, EQ_soc,  -->
<!--          PET_total, -->
<!--          PTP_sim, PTP_rev, PTP_dbl) |> -->
<!--   rename_with(~ str_remove(.x, "_total")) |> -->
<!--   rename_with(~ str_replace(.x, "_", "\n")) %>% -->
<!--   select(order(colnames(.))) |> -->
<!--   correlation() %>% -->
<!--   mutate(across(where(is.numeric), ~ round_half_up(., 2))) |> -->
<!--   summary(redundant = TRUE) |> -->
<!--   plot_cormatrix(fig_cor_subscales) -->

<!-- #p4_t1 -->

<!-- ``` -->

<!-- ```{r fig.height=7.75, fig.width=6.03} -->

<!-- p3_t1 + ggtitle("Correlation histogram") + -->
<!--   p4_t1 + ggtitle("Correlation matrix") +  -->
<!--   plot_layout(ncol = 1, heights = c(.4, 1)) -->

<!-- ggsave_png_pdf("plots/cor_subscales_t1.png", -->
<!--        width = fig_cor_subscales$width, -->
<!--        height = fig_cor_subscales$height, -->
<!--        dpi = 600) -->

<!-- ``` -->

#### Perspective taking (sub)scale correlations

Subset of the (sub)scales that specifically target perspective taking: the IRI Perspective Taking subscale (IRI_PT), the EQ Cognitive empathy subscale (EQ_cog), the Reading the Mind in the Eyes Test (RMET), the Perspective Taking Protocol subscales (PTP_sim/rev/dbl), and the Perspective Taking Task for Adults (PTTA).

```{r fig.height=6, fig.width=11}

pt_cors <- data_sumscores |>
  filter(timepoint == 1) |>
  select(IRI_PT,
         EQ_cog,
         RMET_total,
         PTP_sim, PTP_rev, PTP_dbl,
         PTTA_total) |>
  rename_with(~ str_remove(.x, "_total")) |>
  correlation()

pt_cors |>
  as.data.frame() |>
  select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p) |>
  mutate(p = insight::format_p(p)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

p5_t1 <-
  ggplot(pt_cors, aes(r)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_histogram(binwidth = 0.1, boundary = 0) +
  scale_x_continuous(limits = c(-1, 1),
                     name = "Correlation",
                     breaks = scales::breaks_pretty(n = 10)) +
  scale_y_continuous(name = "Frequency",
                     breaks = scales::breaks_pretty(n = 7)) +
  theme_linedraw(base_size = base_size(fig_cor_pt)) +
  theme(panel.grid.minor.y = element_blank())

#p5_t1

# code repeated in order to use the rename, which screws up the table but is needed for the plot
cormat_pt_t1 <- data_sumscores |>
  filter(timepoint == 1) |>
  # PTP first so it sits at the top-left of the matrix; other measures alphabetical
  select(PTP_sim, PTP_rev, PTP_dbl,
         EQ_cog,
         IRI_PT,
         PTTA_total,
         RMET_total) |>
  rename_with(~ str_remove(.x, "_total")) |>
  rename_with(~ str_replace(.x, "_", "\n")) |>
  correlation() %>%
  #mutate(across(where(is.numeric), ~ round_half_up(., 2))) |>
  summary(redundant = TRUE)

#plot_cormatrix(cormat_pt_t1, fig_cor_pt)

```

```{r fig.height=4.3, fig.width=5.02}

plot_cormatrix(cormat_pt_t1, fig_cor_pt, "Correlation matrix")

ggsave_png_pdf("plots/cor_pt_t1.png",
       width = fig_cor_pt$width,
       height = fig_cor_pt$height,
       dpi = 600)

```

<!-- ### T2 -->

<!-- ```{r} -->

<!-- dat <- data_processed |> -->
<!--   filter(timepoint == 2) -->

<!-- ``` -->

<!-- #### Scale correlations -->

<!-- ```{r fig.height=4.5} -->

<!-- scale_cors <- dat |> -->
<!--   select(SITES, ends_with("_total")) |> -->
<!--   rename_with(~ str_remove(.x, "_total")) %>% -->
<!--   select(order(colnames(.))) |> -->
<!--   correlation() -->

<!-- res <- scale_cors |> -->
<!--   as.data.frame() |> -->
<!--   select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p)  -->

<!-- res |> -->
<!--   mutate(p = insight::format_p(p)) |> -->
<!--   mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |> -->
<!--   kable(align = "r") |> -->
<!--   kable_classic(full_width = FALSE) -->

<!-- p1_t2 <-  -->
<!--   ggplot(res, aes(r)) + -->
<!--   geom_vline(xintercept = 0, linetype = "dashed") + -->
<!--   geom_histogram(binwidth = 0.1, boundary = 0) + -->
<!--   scale_x_continuous(limits = c(-1, 1),  -->
<!--                      name = "Correlation",  -->
<!--                      breaks = scales::breaks_pretty(n = 10)) +  -->
<!--   scale_y_continuous(name = "Frequency",  -->
<!--                      breaks = scales::breaks_pretty(n = 7)) +  -->
<!--   theme_linedraw(base_size = base_size(fig_cor_scales)) + -->
<!--   theme(panel.grid.minor.y = element_blank()) -->

<!-- #p1_t2 -->

<!-- p2_t2 <-  -->
<!--   scale_cors |> -->
<!--   summary(redundant = TRUE) |> -->
<!--   plot_cormatrix(fig_cor_scales) -->

<!-- #p2_t2 + coord_fixed(ratio = 1) -->

<!-- # scale_cors |> -->
<!-- #   summary() |> -->
<!-- #   plot(show_data = "points", -->
<!-- #        stars = FALSE) + -->
<!-- #   theme_linedraw() + -->
<!-- #   ggtitle("") + -->
<!-- #   coord_fixed(ratio = 1) -->

<!-- average_cors_all <- res |> -->
<!--   dplyr::summarize(mean_r = mean(r), -->
<!--                    sd_r = sd(r), -->
<!--                    median_r = median(r), -->
<!--                    mad_r = mad(r), -->
<!--                    min_r = min(r), -->
<!--                    max_r = max(r))  -->

<!-- average_cors_all |> -->
<!--   round_half_up(digits = 2) |> -->
<!--   kable() |> -->
<!--   kable_classic(full_width = FALSE) -->

<!-- ``` -->

<!-- ```{r fig.height=7.32, fig.width=6.27} -->

<!-- p1_t2 + ggtitle("Correlation histogram") + -->
<!--   p2_t2 + ggtitle("Correlation matrix") +  -->
<!--   plot_layout(ncol = 1, heights = c(.4, 1)) -->

<!-- ggsave_png_pdf("plots/cor_scales_t2.png", -->
<!--        width = fig_cor_scales$width, -->
<!--        height = fig_cor_scales$height, -->
<!--        dpi = 600) -->

<!-- ``` -->

<!-- #### Subscale correlations -->

<!-- ```{r fig.height=6, fig.width=11} -->

<!-- subscale_cors <- dat |> -->
<!--   select(SITES,  -->
<!--          IRI_FS, IRI_EC, IRI_PT, IRI_PD,  -->
<!--          EQ_cog, EQ_aff, EQ_soc,  -->
<!--          PET_total, -->
<!--          RMET_total) |> -->
<!--   rename_with(~ str_remove(.x, "_total")) |> -->
<!--   correlation()  -->

<!-- subscale_cors |> -->
<!--   as.data.frame() |> -->
<!--   select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p) |> -->
<!--   mutate(p = insight::format_p(p)) |> -->
<!--   mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |> -->
<!--   kable(align = "r") |> -->
<!--   kable_classic(full_width = FALSE) -->

<!-- p3_t2 <-  -->
<!--   ggplot(subscale_cors, aes(r)) + -->
<!--   geom_vline(xintercept = 0, linetype = "dashed") + -->
<!--   geom_histogram(binwidth = 0.1, boundary = 0) + -->
<!--   scale_x_continuous(limits = c(-1, 1),  -->
<!--                      name = "Correlation",  -->
<!--                      breaks = scales::breaks_pretty(n = 10)) +  -->
<!--   scale_y_continuous(name = "Frequency",  -->
<!--                      breaks = scales::breaks_pretty(n = 7)) +  -->
<!--   theme_linedraw(base_size = base_size(fig_cor_subscales)) + -->
<!--   theme(panel.grid.minor.y = element_blank()) -->

<!-- #p3_t2 -->

<!-- # code repeated in order to use the rename, which screws up the table but is needed for the plot -->
<!-- p4_t2 <- dat |> -->
<!--   select(SITES,  -->
<!--          IRI_FS, IRI_EC, IRI_PT, IRI_PD,  -->
<!--          EQ_cog, EQ_aff, EQ_soc,  -->
<!--          PET_total, -->
<!--          RMET_total) |> -->
<!--   rename_with(~ str_remove(.x, "_total")) |> -->
<!--   rename_with(~ str_replace(.x, "_", "\n")) %>% -->
<!--   select(order(colnames(.))) |> -->
<!--   correlation() %>% -->
<!--   mutate(across(where(is.numeric), ~ round_half_up(., 2))) |> -->
<!--   summary(redundant = TRUE) |> -->
<!--   plot_cormatrix(fig_cor_subscales) -->

<!-- #p4_t2 -->

<!-- ``` -->

<!-- ```{r fig.height=7.75, fig.width=6.03} -->

<!-- p3_t2 + ggtitle("Correlation histogram") + -->
<!--   p4_t2 + ggtitle("Correlation matrix") +  -->
<!--   plot_layout(ncol = 1, heights = c(.4, 1)) -->

<!-- ggsave_png_pdf("plots/cor_subscales_t2.png", -->
<!--        width = fig_cor_subscales$width, -->
<!--        height = fig_cor_subscales$height, -->
<!--        dpi = 600) -->

<!-- ``` -->

<!-- ### Both times - scales -->

<!-- ```{r fig.height=4.02, fig.width=6.27} -->

<!-- p1_t1 + ggtitle("Correlation histogram (T1)") + -->
<!--   p1_t2 + ggtitle("Correlation matrix (T2)") +  -->
<!--   p2_t1 + ggtitle("Correlation histogram (T1)") + -->
<!--   p2_t2 + ggtitle("Correlation matrix (T2)") +  -->
<!--   plot_layout(ncol = 2, heights = c(.4, 1), guides = "collect") -->

<!-- # NB the panels above were built at the scale of the portrait figures; rebuild -->
<!-- # them with plot_cormatrix(..., fig_cor_both) if this figure is re-enabled -->
<!-- ggsave_png_pdf("plots/cor_scales_both.png", -->
<!--        width = fig_cor_both$width, -->
<!--        height = fig_cor_both$height, -->
<!--        dpi = 600) -->

<!-- ``` -->

<!-- ### Both times - subscales -->

<!-- ```{r fig.height=4.27, fig.width=6.27} -->

<!-- p3_t1 + ggtitle("Correlation histogram (T1)") + -->
<!--   p3_t2 + ggtitle("Correlation matrix (T2)") +  -->
<!--   p4_t1 + ggtitle("Correlation histogram (T1)") + -->
<!--   p4_t2 + ggtitle("Correlation matrix (T2)") +  -->
<!--   plot_layout(ncol = 2, heights = c(.4, 1), guides = "collect") -->

<!-- # NB the panels above were built at the scale of the portrait figures; rebuild -->
<!-- # them with plot_cormatrix(..., fig_cor_both_sub) if this figure is re-enabled -->
<!-- ggsave_png_pdf("plots/cor_subscales_both.png", -->
<!--        width = fig_cor_both_sub$width, -->
<!--        height = fig_cor_both_sub$height, -->
<!--        dpi = 600) -->

<!-- ``` -->


# Session info

```{r}

sessionInfo()

```



